Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-15 talk/pepm2011/paper.tex
add lifting example

XXX Apply the rules of the algorithm to parts of the sample trace

>>>>

As an example for lifting, consider the static heap $$\{v^* \mapsto (T_1, w^*,
v^*), w^* \mapsto (T_2, u^*, u^*)\}$$ which contains two static objects. If $v^*$
now needs to be lifted, the following residual operations are produced:

\begin{lstlisting}[mathescape,xleftmargin=20pt]
$v^*$ = new($T_1$)
$w^*$ = new($T_2$)
set($w^*$, $L$, $u^*$)
set($w^*$, $R$, $u^*$)
set($v^*$, $L$, $w^*$)
set($v^*$, $R$, $v^*$)
\end{lstlisting}

After the lifting the static heap is the empty set, because both static objects
were lifted.
